CUNY SPS DATA-607 Week 1 Assignment

### 2018-08-28 DATA607/Week 1 Assignment/Week_1_Assignment.Rmd
More work on DATA 607 Week 1 Assignment

---
title: "CUNY SPS DATA-607 Week 1 Assignment"
subtitle: "Loading Data into a Data Frame"
author: "Mike Silva"
date: "August 27, 2018"
output:
  html_document:
    keep_md: yes
---

@@

```{r rename-columns, warning=FALSE}
library(dplyr)

>>>>

---
title: "CUNY SPS DATA-607 Week 1 Assignment"
subtitle: "Loading Data into a Data Frame"
author: "Mike Silva"
date: "August 27, 2018"
---

@@

```{r rename-columns, warning=FALSE, message=FALSE}
library(dplyr)
